Example

### 2020-12-30 example.rmd
example running ok again

```{r GR_results}
datR <- read.table("data/data_repeat.txt",header=TRUE)
datR$obs <- factor(seq(nrow(datR)))
datR <- (datR 
  %>% mutate(sp = species
        , animals = phylo
        )
)
datR$spec_mean_cf <- sapply(split(datR$cofactor,datR$phylo),mean)[datR$phylo]
datR$within_spec_cf <- datR$cofactor-datR$spec_mean_cf
phylo_lmm_fit <- phylo_lmm(phen~spec_mean_cf+within_spec_cf+(1|sp) + (1|animals)
  , data=datR
  , phylonm = "sp"
  , phylo = phylo
  , phyloZ=phyloZ
  , REML = FALSE
  , control=lmerControl(check.nobs.vs.nlev="ignore",check.nobs.vs.nRE="ignore")
)

@@

dat <- dat %>% mutate(sp=phylo) 
phylo_glmm_fit <- phylo_glmm(phen_pois~cofactor+(1|sp)+(1|obs)
  , data=dat
  , phylonm = "sp"
  , family = poisson
  , phylo = phylo
  , phyloZ=phyloZ
  , control=lmerControl(check.nobs.vs.nlev="ignore",check.nobs.vs.nRE="ignore")
)

>>>>

```{r GR_results}
datR <- read.table("data/data_repeat.txt",header=TRUE)
datR$obs <- factor(seq(nrow(datR)))
datR <- (datR 
  %>% mutate(sp = factor(species)
        , animals = factor(phylo)
        )
)
datR$spec_mean_cf <- sapply(split(datR$cofactor,datR$phylo),mean)[datR$phylo]
datR$within_spec_cf <- datR$cofactor-datR$spec_mean_cf
phylo_lmm_fit <- phylo_lmm(phen~spec_mean_cf+within_spec_cf+(1|sp) + (1|animals)
  , data=datR
  , phylonm = "sp"
  , phylo = phylo
  , phyloZ=phyloZ
  , REML = FALSE
  , control=lmerControl(check.nobs.vs.nlev="ignore",check.nobs.vs.nRE="ignore")
)

@@

dat <- dat %>% mutate(sp=factor(phylo)) 
phylo_glmm_fit <- phylo_glmm(phen_pois~cofactor+(1|sp)+(1|obs)
  , data=dat
  , phylonm = "sp"
  , family = poisson
  , phylo = phylo
  , phyloZ=phyloZ
  , control=lmerControl(check.nobs.vs.nlev="ignore",check.nobs.vs.nRE="ignore")
)
